Storing messages with multipartite neural cliques

### 2014-07-22 Articles/article.tex
amélioration figure 1

\begin{figure}[!h]
\centering
\begin{tikzpicture}
  \foreach \type/\fill/\xshift/\yshift in {circle/draw/-50pt/50pt,rectangle/draw/50pt/50pt,rectangle/fill/-50pt/-50pt,circle/fill/50pt/-50pt}{
    \begin{scope}[xshift=\xshift,yshift=\yshift]
    \tikzstyle{every node}=[\type,draw,\fill];
    \foreach \i in {0,20pt,40pt,60pt}{
      \foreach \j in {0,20pt,40pt,60pt}{
        \node (node\type\fill\i\j) at (\i,\j) {};
      }
    }
\end{scope}
  }
  %% \path
  %% (nodecircledraw20pt40pt) edge (nodecirclefill040pt)
  %% edge (noderectanglefill20pt20pt)
  %% edge (noderectangledraw60pt60pt)
  %% (nodecirclefill040pt) edge (noderectanglefill20pt20pt)
  %% edge (noderectangledraw60pt60pt)
  %% (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
  %% ;
  %% \path
  %% (nodecircledraw60pt60pt) edge (nodecirclefill40pt20pt)
  %% edge (noderectanglefill060pt)
  %% edge (noderectangledraw20pt40pt)
  %% (nodecirclefill40pt20pt) edge (noderectanglefill060pt)
  %% edge (noderectangledraw20pt40pt)
  %% (noderectanglefill060pt) edge (noderectangledraw20pt40pt)
  %% ;
  \path[thick]
  %%%%
  (nodecircledraw40pt60pt) edge (nodecirclefill20pt20pt)
  edge (noderectanglefill40pt60pt)
  edge (noderectanglefill20pt20pt)
  edge (noderectangledraw40pt20pt)
  edge (nodecirclefill60pt60pt)
  %edge (noderectanglefill40pt40pt)
  edge (noderectangledraw60pt60pt)
  %%%%%%%%%%%
  (nodecircledraw020pt) edge (nodecirclefill20pt20pt)
  edge (noderectanglefill40pt60pt)
  edge (noderectanglefill20pt20pt)
  edge (noderectangledraw40pt20pt)
  edge (nodecirclefill60pt60pt)
  %edge (noderectanglefill40pt40pt)
  edge (noderectangledraw60pt60pt)
  %%%%%%%%%%%%%%
  (nodecirclefill20pt20pt) edge (noderectanglefill40pt60pt)
  edge (noderectangledraw60pt60pt)
  edge (noderectanglefill20pt20pt)
  edge (noderectangledraw40pt20pt)
  %%%%%
  (nodecirclefill60pt60pt) edge (noderectanglefill40pt60pt)
  edge (noderectangledraw60pt60pt)
  edge (noderectanglefill20pt20pt)
  edge (noderectangledraw40pt20pt)
  %%%%%
  (noderectanglefill40pt60pt) edge (noderectangledraw60pt60pt)
  edge (noderectangledraw40pt20pt)
  %%%%%%%%%%%
  (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
  edge (noderectangledraw40pt20pt)
  ;
\end{tikzpicture}
\caption{Illustration of the storage process of a message $\mu$. In this setting the number of clusters is $c=4$, each containing $\ell=16$ units. The parameter $a$ is 2.}
\label{fig:storage}
\end{figure}

@@

	Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent, 
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/c5l256densities}%remplacement_densite_c8l256a4}
		\caption{Theoretical and empirical densities for networks of 5 clusters, 256 units per cluster }
			\label{densiteth}
	\end{figure}

>>>>

\begin{figure}[!h]
\centering
\begin{tikzpicture}
  \foreach \type/\fill/\xshift/\yshift in {circle/draw/-50pt/50pt,rectangle/draw/50pt/50pt,rectangle/fill/-50pt/-50pt,circle/fill/50pt/-50pt}{
    \begin{scope}[xshift=\xshift,yshift=\yshift]
    \tikzstyle{every node}=[\type,draw,\fill];
    \foreach \i in {0,20pt,40pt,60pt}{
      \foreach \j in {0,20pt,40pt,60pt}{
        \node (node\type\fill\i\j) at (\i,\j) {};
      }
    }
\end{scope}
  }
  %% \path
  %% (nodecircledraw20pt40pt) edge (nodecirclefill040pt)
  %% edge (noderectanglefill20pt20pt)
  %% edge (noderectangledraw60pt60pt)
  %% (nodecirclefill040pt) edge (noderectanglefill20pt20pt)
  %% edge (noderectangledraw60pt60pt)
  %% (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
  %% ;
  %% \path
  %% (nodecircledraw60pt60pt) edge (nodecirclefill40pt20pt)
  %% edge (noderectanglefill060pt)
  %% edge (noderectangledraw20pt40pt)
  %% (nodecirclefill40pt20pt) edge (noderectanglefill060pt)
  %% edge (noderectangledraw20pt40pt)
  %% (noderectanglefill060pt) edge (noderectangledraw20pt40pt)
  %% ;
  \path[thick]
  %%%%
  (nodecircledraw40pt60pt) edge (nodecirclefill20pt20pt)
  edge (noderectanglefill20pt60pt)
  edge (noderectanglefill60pt20pt)
  edge (noderectangledraw60pt20pt)
  edge (nodecirclefill60pt60pt)
  %edge (noderectanglefill40pt40pt)
  edge (noderectangledraw20pt60pt)
  %%%%%%%%%%%
  (nodecircledraw020pt) edge (nodecirclefill20pt20pt)
  edge (noderectanglefill20pt60pt)
  edge (noderectanglefill60pt20pt)
  edge (noderectangledraw60pt20pt)
  edge (nodecirclefill60pt60pt)
  %edge (noderectanglefill40pt40pt)
  edge (noderectangledraw20pt60pt)
  %%%%%%%%%%%%%%
  (nodecirclefill20pt20pt) edge (noderectanglefill20pt60pt)
  edge (noderectangledraw20pt60pt)
  edge (noderectanglefill60pt20pt)
  edge (noderectangledraw60pt20pt)
  %%%%%
  (nodecirclefill60pt60pt) edge (noderectanglefill20pt60pt)
  edge (noderectangledraw60pt20pt)
  edge (noderectanglefill60pt20pt)
  edge (noderectangledraw20pt60pt)
  %%%%%
  (noderectanglefill20pt60pt) edge (noderectangledraw20pt60pt)
  edge (noderectangledraw60pt20pt)
  %%%%%%%%%%%
  (noderectanglefill60pt20pt) edge (noderectangledraw20pt60pt)
  edge (noderectangledraw60pt20pt)
  ;
\end{tikzpicture}
\caption{Illustration of the storage process of a message $\mu$. In this setting the number of clusters is $c=4$, each containing $\ell=16$ units. The parameter $a$ is 2.}
\label{fig:storage}
\end{figure}

@@

	Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent, 
	The higher $a$ is, the quicker density approaches $1$.

	Multipartite cliques saturate quicker.

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/c5l256densities}%remplacement_densite_c8l256a4}
		\caption{Theoretical and empirical densities for networks of 5 clusters, 256 units per cluster }
			\label{densiteth}
	\end{figure}
